Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-15 manuscript/manuscript.Rmd
threshold comment

The policies explored were functions from states $N_t$ to a single number, $M_X(N_t) = \pi_\theta(N_t)$, in the single fishery case.
In the two-fishery case, policies lead to two-dimensional actions: $(M_X(N_t), M_Y(N_t)) = \pi_\theta(N_t)$.
Each episode in the training and in the evaluation stages was at most 200 time steps long.
Episodes were ended early in case of a ‘‘near-extinction event,’’ a moment in which any of the populations dipped below a threshold value, i.e.,
\begin{align}
  \label{eq:thresh}
  X_t \leq X_{\text{thresh.}},\quad
  Y_t \leq Y_{\text{thresh.}},\quad
  \text{or,}\quad
  Z \leq Z_{\text{thresh.}}.
\end{align}
The reward function had two componenets:
First, at each time step the harvest $h_t$ was received as a reward.
Second, if the episode ended early (say, at time-step $t$) because of a near-extinction event, a negative reward of $-100/t$ was awarded.
This reward function balances the extractive motivation of the fishery with conservation goals that go beyond the scope of long-term sustainable harvests.

>>>>

The policies explored were functions from states $N_t$ to a single number, $M_X(N_t) = \pi_\theta(N_t)$, in the single fishery case.
In the two-fishery case, policies lead to two-dimensional actions: $(M_X(N_t), M_Y(N_t)) = \pi_\theta(N_t)$.
Each episode in the training and in the evaluation stages was at most 200 time steps long.
Episodes were ended early in case of a ‘‘near-extinction event,’’ a moment in which any of the populations dipped below a threshold value, i.e.,
\begin{align}
  \label{eq:thresh}
  X_t \leq X_{\text{thresh.}},\quad
  Y_t \leq Y_{\text{thresh.}},\quad
  \text{or,}\quad
  Z \leq Z_{\text{thresh.}}.
\end{align}
For a realistic fishery model, this threshold value could represent a population value beyond which drastic ecological consequences may ensue, e.g. a tipping point.
In our setting we have chosen $X_{\text{thresh.}}=Y_{\text{thresh.}}=Z_{\text{thresh.}}=0.05$ as a rule of thumb---given that under natural (unharvested) dynamics the populations range within values of 0.5 to 1, this would represent on the order of a 90% population decrease from its ‘‘natural’’ level.

The reward function had two componenets:
First, at each time step the harvest $h_t$ was received as a reward.
Second, if the episode ended early (say, at time-step $t$) because of a near-extinction event, a negative reward of $-100/t$ was awarded.
This reward function balances the extractive motivation of the fishery with conservation goals that go beyond the scope of long-term sustainable harvests.
